---
title: "RegressionSummary"
author: "David"
date: "2024-03-21"
output: pdf_document
---

```{r, include = FALSE}

library(lfe)
library(tidyverse)
library(DescTools)

subset_largestsublist <- read_csv("~/Desktop/Portfolio_Trades_my_computer/data_minimizing/regression20.03/subset_largestsublist.csv")
subset_allothersublist <- read_csv("~/Desktop/Portfolio_Trades_my_computer/data_minimizing/regression20.03/subset_allothersublist.csv")
subset <- read_csv("~/Desktop/Portfolio_Trades_my_computer/data_minimizing/regression20.03/trans_cost_calc.csv")
```



## Regression functions

```{r}
Regression1 <-  function(df) {
  
  regr1 <- felm(filled ~ trans_cost + mediancost_insublist +
                  mediancost_outsidesublist | req_id | 0 | req_id, data = df)
  summary_regr1 <- summary(regr1, cluster = c("req_id"))
  return(summary_regr1)
}
#regression2: filled ~ trans_cost mincost_insublist mincost_outsidesublist
Regression2 <- function(df){
  
  regr2 <- felm(filled ~ trans_cost + mincost_insublist + 
                  mincost_outsidesublist | req_id | 0 | req_id, data = df)
  summary_regr2 <- summary(regr2, cluster = c("req_id"))
  
  return(summary_regr2)
}
winsorize_trans_cost <- function(df){
    df$trans_cost <- Winsorize(df$trans_cost, minval = quantile(df$trans_cost, 0.005, na.rm = TRUE), maxval = quantile(df$trans_cost, 0.995, na.rm=TRUE), na.rm = TRUE)
    return(df)
    }

```


## Winsorizing trans_cost data

```{r}
subset_allothersublist <- winsorize_trans_cost(subset_largestsublist)
subset_largestsublist <- winsorize_trans_cost(subset_allothersublist)
```



## Detailed summary of trans_cost

```{r}
sum_stats_sub <- subset%>%
  summarise(
    Mean = mean(    trans_cost,       na.rm = TRUE) %>% round(3),
    SD   = sd(      trans_cost,       na.rm = TRUE) %>% round(3),
    p1   = quantile(trans_cost, 0.01, na.rm = TRUE) %>% round(3),
    p5   = quantile(trans_cost, 0.05, na.rm = TRUE) %>% round(3),
    p10  = quantile(trans_cost, 0.10, na.rm = TRUE) %>% round(3),
    p50  = quantile(trans_cost, 0.50, na.rm = TRUE) %>% round(3),
    p90  = quantile(trans_cost, 0.90, na.rm = TRUE) %>% round(3),
    p95  = quantile(trans_cost, 0.95, na.rm = TRUE) %>% round(3),
    p99  = quantile(trans_cost, 0.99, na.rm = TRUE) %>% round(3))
sum_stats_sub
```


## Regression1 on subset_largestsublist

```{r}
summary1_largestsublist <- Regression1(subset_largestsublist)
print(summary1_largestsublist)
```


## Regression2 on subset_largestsublist

```{r}
summary2_largestsublist <- Regression2(subset_largestsublist)
print(summary2_largestsublist)
```


## Regression1 on subset_allothersublist

```{r}
summary1_allothersublist <- Regression1(subset_allothersublist)
print(summary1_allothersublist)
```


## Regression2 on subset_allothersublist

```{r}
summary2_allothersublist <- Regression2(subset_allothersublist)
print(summary2_allothersublist)
```




## Simple regression model of filled on trans_cost for non-dealer HY requests 
## *without list fixed effects*
```{r}
model1_fe <- lm(filled ~ trans_cost, data = subset_largestsublist)
summary(model1_fe)
```

## Simple regression model of filled on trans_cost for non-dealer HY requests 
## *with list fixed effects*

This is run with felm, because lm with req_id fixed effect is computationally 
very intensive (vector memory is exceeded)
```{r}
model2_nofe <- felm(filled ~ trans_cost | req_id, data = subset_largestsublist)
summary(model2_nofe)
```

